### 2019-02-14 Sections/costs_and_attributes_in_quantum_networks.tex
minor

\begin{figure}[!htbp]
% \includegraphics[clip=true, width=0.3\textwidth]{data_proc_ineq}
\end{figure}

@@

\begin{widetext}\vspace{1cm}
\begin{table}[t]
\begin{tabular}{ |c | c | c| c| } \hline
Capacity & Type of information & Correlation measure &Capacity formula  \\ \hline
Classical &Classical information &Holevo information &Eq.~(\ref{eq:holevoinfo})       \\
Private & Classical information & Private information  & See Ref.~\cite{bib:PhysRevLett.103.120501} \\
Entanglement Assisted Classical & Classical information & Quantum mutual information & See Ref.~\cite{bib:PhysRevLett.83.3081} \\
Quantum &Quantum information &Quantum Coherent Information &Eq.~(\ref{eq:quantcohinfo}) \\ \hline
\end{tabular}
\caption{\label{tab:capacities} Measure of classical and quantum channel capacities.}
\end{table}\vspace{1cm}
\end{widetext}

@@

One of the channels is a 50$\%$ erasure channel (which we know to have zero quantum capacity from the non-cloning theroem), and the other is known as an entanglement-binding channel (
see Ref~\cite{horodecki2001separability} for details of such a channel).

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{data_proc_ineq}
\end{figure}

@@

\begin{widetext}\vspace{1cm}
\begin{table}[t]
\begin{tabular}{ |c | c | c| c| } \hline
Capacity & Type of information & Correlation measure &Capacity formula  \\ \hline
Classical &Classical information &Holevo information &Eq.~(\ref{eq:holevoinfo})       \\
Private & Classical information & Private information  & See Ref.~\cite{bib:PhysRevLett.103.120501} \\
Entanglement Assisted Classical & Classical information & Quantum mutual information & See Ref.~\cite{bib:PhysRevLett.83.3081} \\
Quantum &Quantum information &Quantum Coherent Information &Eq.~(\ref{eq:quantcohinfo}) \\ \hline
\end{tabular}
\caption{\label{tab:capacities} Measure of classical and quantum channel capacities. Taken from \cite{bib:8242350}}
\end{table}\vspace{1cm}
\end{widetext}

@@

One of the channels is a 50$\%$ erasure channel (which we know to have zero quantum capacity from the non-cloning theroem), and the other is known as an entanglement-binding channel (see \cite{horodecki2001separability} for details of such a channel).
